---
title: " "
---

```{r setup}
#| include: false

projects <- list(

  list(
    title = "The Geography of Cooling",
    image = "images/evap-cooling.jpg",
    brief = "Household-level spatial dataset of evaporative cooler adoption in a US city. Five studies examining cooling equity, urban heat exposure, monsoon vulnerability, climate adaptation, and health outcomes in Tucson.",
    pdf = "",
    website = "https://scorch-idvc.github.io/evap-cooling/"
  ),

  list(
    title = "Project Title 2",
    image = "images/placeholder.jpg",
    brief = "Brief description of the project. What question does it answer? What data does it use? Who benefits from the results?",
    pdf = "files/project2.pdf",
    website = ""
  )
)

members <- list(

  list(
    name = "Name 1",
    position = "XX",
    role = "IDVC Director",
    description = "Bio.",
    website = "",
    email = "member1@arizona.edu"
  ),

  list(
    name = "Member Name 2",
    position = "XX",
    role = "Data Visualization",
    description = "Bio.",
    website = "",
    email = "member2@arizona.edu"
  ),

  list(
    name = "Member 3",
    position = "XX",
    role = "Data Management",
    description = "Bio.",
    website = "",
    email = "member3@arizona.edu"
  )

)
```

::: {.hero}
[SCORCH | Integrated Data Visualization Core]{.acronym}

# Data for *resilient* communities

We support climate and health research in arid lands in the southwest of the USA through data science, visualization, and training. Our work helps researchers, communities, and decision-makers understand and respond to the health impacts of a warming climate.
:::


<!-- ============================================================ -->
<!-- ABOUT -->
<!-- ============================================================ -->

::: {.section-header}
::: {.section-bar}
:::
## About IDVC
:::

::: {.about-section}
The Southwest Center on Resilience for Climate Change and Health (SCORCH) brings together transdisciplinary research groups to conduct solutions-oriented team-science projects responsive to the health needs of arid lands communities adapting to climate change. The Integrated Data Visualization Core (IDVC) supports the overall Center mission through the provision of data science, visualization, and management expertise.
:::

::: {.services}
::: {.service-box}
::: {.service-num}
1
:::
#### Data management
Sharing, analyses, and stewardship congruent with scientific data management best practices.
:::
::: {.service-box}
::: {.service-num}
2
:::
#### Visualization
Interactive tools and figures that make integrated health and climate data accessible to researchers and communities.
:::
::: {.service-box}
::: {.service-num}
3
:::
#### Training
Workshops and resources to develop and enhance capacity to manage and visualize integrated health and climate data.
:::
:::


<!-- ============================================================ -->
<!-- PROJECTS -->
<!-- ============================================================ -->

::: {.section-header #projects}
::: {.section-bar}
:::
## Projects
What we are working on.
:::

```{r projects}
#| output: asis
#| echo: false

cat('<div class="cards-grid">\n')

for (proj in projects) {
  cat('<div class="project-card">\n')

  ## Image
  if (nzchar(proj$image) && file.exists(proj$image)) {
    cat(sprintf('  <img src="%s" alt="%s">\n', proj$image, proj$title))
  } else {
    ## Placeholder gradient if no image
    cat(sprintf('  <div style="width:100%%;height:180px;background:#e4f0e7;display:flex;align-items:center;justify-content:center;font-family:Fraunces,serif;font-size:1.2rem;color:#8a7d6b;">%s</div>\n',
                substr(proj$title, 1, 30)))
  }

  cat('  <div class="card-body">\n')
  cat(sprintf('    <h3>%s</h3>\n', proj$title))
  cat(sprintf('    <p>%s</p>\n', proj$brief))

  ## Links
  cat('    <div class="card-links">\n')
  if (nzchar(proj$pdf)) {
    cat(sprintf('      <a href="%s" class="link-pdf" target="_blank">PDF</a>\n', proj$pdf))
  }
  if (nzchar(proj$website)) {
    cat(sprintf('      <a href="%s" class="link-web" target="_blank">Website</a>\n', proj$website))
  }
  cat('    </div>\n')

  cat('  </div>\n')
  cat('</div>\n')
}

cat('</div>\n')
```


<!-- ============================================================ -->
<!-- TEAM -->
<!-- ============================================================ -->

::: {.section-header #team}
::: {.section-bar}
:::
## Team
The people behind the work.
:::

```{r members}
#| output: asis
#| echo: false

cat('<div class="cards-grid">\n')

for (m in members) {
  ## Initials for avatar
  initials <- paste(
    sapply(strsplit(m$name, " ")[[1]], function(w) substr(w, 1, 1)),
    collapse = "")

  cat('<div class="member-card">\n')
  cat(sprintf('  <div class="avatar">%s</div>\n', initials))
  cat(sprintf('  <h3>%s</h3>\n', m$name))
  cat(sprintf('  <div class="position">%s</div>\n', m$position))
  cat(sprintf('  <div class="role">%s</div>\n', m$role))
  cat(sprintf('  <p>%s</p>\n', m$description))

  cat('  <div class="member-links">\n')
  if (nzchar(m$website)) {
    cat(sprintf('    <a href="%s" target="_blank">Website</a>\n', m$website))
  }
  if (nzchar(m$email)) {
    cat(sprintf('    <a href="mailto:%s">Email</a>\n', m$email))
  }
  cat('  </div>\n')

  cat('</div>\n')
}

cat('</div>\n')
```


<!-- ============================================================ -->
<!-- CONTACT -->
<!-- ============================================================ -->

::: {.section-header #contact}
::: {.section-bar}
:::
:::

::: {.contact-section}
## Get in touch

The IDVC is part of the Southwest Center on Resilience for Climate Change and Health (SCORCH) at the University of Arizona. We enhance institutional capacity to conduct climate change and health research tailored to the needs of arid lands communities.

[XX@arizona.edu](mailto:XX@arizona.edu)
:::

::: {.site-footer}
SCORCH | Integrated Data Visualization Core | University of Arizona
:::
